---
title: "imaging the influence of certainty and value on spatial attention - (second) pilot data analysis"
author: "Kelly Garner"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "getkellygarner@gmail.com"
github: "kel-github"

output:
  epuRate::epurate:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---


<br><br>

> Initial analysis of the behavioural data collected on a simple paradigm where simple cues (e.g. square, triangle, circle) probabilistically predict the upcoming target location (gabor oriented clockwise or counterclockwise) and the reward value available should the participant got the target correct. [All data was collected using this code](https://github.com/kel-github/imaging-cert-reward-att-task-code/tree/master/pilot_expCues).


# Get the data
***
Starting by loading *libraries*. 
```{r, message=FALSE, warning=FALSE}
library(rmarkdown)    # You need this library to run this template.
library(epuRate) 
#library(tidyverse)
library(tidyr)
library(dplyr)
library(cowplot)
library(ggplot2)
library(readr)
library(wesanderson)
#library(rjson)
library(RJSONIO)
source("R_rainclouds.R") # for the raincloud plot
```

Hidden code below defines plotting functions.
```{r}
line.plot <- function(data, dv, iv, grp, ylims, cols){
          ggplot(data, aes_string(x=iv, y=dv, col=grp)) +
            geom_line(aes_string(group=grp)) + geom_point() +
            facet_wrap(~sub, nrow=1) +  
            scale_fill_manual(values=cols) +
            scale_color_manual(values=cols) + 
            ylab(dv) + xlab(iv) + ylim(ylims) +
            theme(panel.border = element_blank(), 
                  panel.grid.major =   element_blank(),
            panel.grid.minor = element_blank(), 
            axis.line = element_line(colour = "black"))
}


```
Here is the behavioural data in longform. 
Key to data:
sub = subject number, sess = session number, t = trial, rew = cue value, loc = target location, 
cue = shape, co1/co2 = contrast of the target on left and right, or = orientation (0 = anti, 1 = clockwise)
response = correct (1) or incorrect (0), rt = RT, rew_tot = reward value accrued, cert = probability of target location, given the cue

```{r}

get_participant_data <- function(subjects, sessions, data_path) {
  # this function loads each participant's data
  # and concatenates them into a longform dataset
  fn <- 'sub-0%d_ses-%d_task-learn-att-v1-test-v1_events.tsv'
  get_subject_strings <- function(i) {
    get_session_strings <- function(j) dir(sprintf(paste(data_path, "sub-0%d_ses-%d_task-learn-att-v1", sep = "/"), i, j), pattern=sprintf(fn, i, j), full.names = TRUE)
    do.call(cbind, lapply(sessions, get_session_strings))
  }
  files <- do.call(rbind, lapply(subjects, get_subject_strings))
  rownames(files) <- subjects
  colnames(files) <- sessions
  resplog <- function(i, j) read.table(files[as.character(i),as.character(j)], sep = "\t", header = TRUE)
  d <- do.call(rbind, lapply(subjects, function(i) do.call(rbind, lapply(sessions, function (j) resplog(i, j)))))
  
  # get trials to getthe reward condition 
  fn <- 'sub-0%d_ses-%d_task-learn-att-v1-test-v1_trls.csv'
  files <- do.call(rbind, lapply(subjects, get_subject_strings))      
  rownames(files) <- subjects
  colnames(files) <- sessions
  eventlog <- function(i, j) {
    e = read.table(files[as.character(i),as.character(j)], sep = ",", header = TRUE)
    e$sub = i
    e$sess= j
    e
  }
  e <- do.call(rbind, lapply(subjects, function(i) do.call(rbind, lapply(sessions, function (j) eventlog(i, j)))))
  names(e)[1] = "t"
  e <- e[, -c(2, 4:8 )]  
  d <- inner_join(d, e, by=c("sub", "sess", "t"))
  # ALLOCATE CUES
  # 1 = left arrow, 2 = right arrow, 3 = bidirectional arrow
  d$cert <- NA
  d$cert[ d$loc == 1 & d$cue == 1 ] = ".8"
  d$cert[ d$loc == 2 & d$cue == 1 ] = ".2"
  d$cert[ d$loc == 2 & d$cue == 2 ] = ".8"
  d$cert[ d$loc == 1 & d$cue == 2 ] = ".2"  
  d$cert[ d$cue == 3 ] = ".5"
  d$cert <- as.factor(d$cert)
  
  d$loc <- as.factor(d$loc)
  levels(d$loc) <- c("left", "right")
  d$sub <- as.factor(d$sub)
  d$rew <- as.factor(d$rew)
  levels(d$rew) <- c("0", "50")
  d$reward_type <- as.factor(d$reward_type)
  levels(d$reward_type) <- c("hh", "hl", "ll", "lh")
  
  d$tgt_value = NA
  d$tgt_value[d$reward_type == "hh" | d$reward_type == "hl"] = "high"
  d$tgt_value[d$reward_type == "ll" | d$reward_type == "lh"] = "low"
  
  d$cue_cond = NA
  d$cue_cond[d$cert == ".5"] = "Hn,Ln"
  d$cue_cond[d$cert == ".8" & d$tgt_value == "high" | d$cert == ".2" & d$tgt_value == "low"] = "Hv,Li"
  d$cue_cond[d$cert == ".2" & d$tgt_value == "high" | d$cert == ".8" & d$tgt_value == "low"] = "Lv,Hi"  
  # set cueing x value factor
  d <- d %>% filter(t > 120) # get rid of the first block of trials
  
  d
}

subjects = c(1, 2, 3)
sessions = 1
data_path = "~/Dropbox/MC-Projects/imaging-value-cert-att/pilot_data/pilot_expCues"
raw.data <- get_participant_data(subjects, sessions, data_path)

# Show it:
raw.data %>% head(5)
```


# Overview of individual subject data
***
These [raincloud plots](https://micahallen.org/2018/03/15/introducing-raincloud-plots/) show individual subject RT distributions (rows) for each level of cue certainty (y-axis), for each level of reward value (5 vs 50, orange and purple distributions respectively).  

## subject level raincloud plots

```{r, warning=FALSE, fig.align='center'}
get.sub.data <- function(subject, data, sd_reject=2.5, RT_min=0.1){
  # this function takes the subject index (defined in the variable subject)
  # and all the raw data
  # it filters the data to get the individual subject's data, then trims to
  # get the correct RTs that are > .1 s, and are < 3 * sd from the median
  # for each certainty and reward condition
  sub.data <- data %>% filter(sub == subject)
  sub.data <- sub.data %>% 
                filter(rt > RT_min) %>%
                filter(resp == 1) %>%
                group_by(cert, tgt_value, cue_cond) %>%
                filter(rt < median(rt) + sd_reject*sd(rt)) 
}
# apply the function defined above across subjects, put
# results into a single dataframe
subjects = c("1", "2", "3")  
sub.data <- lapply(subjects, get.sub.data, data = raw.data)
sub.data <- do.call(rbind, sub.data)  

```

## summary plots
To better visualise the influence of certainty and value, I now show the inverse efficiency score (RT/accuracy, see [Gould et al, 2011](https://www.physiology.org/doi/full/10.1152/jn.00653.2010?url_ver=Z39.88-2003&rfr_id=ori%3Arid%3Acrossref.org&rfr_dat=cr_pub%3Dpubmed&)) for each participant.

```{r, warning=FALSE, fig.align='center' }

acc.data = raw.data %>% group_by(sub, tgt_value, cue_cond) %>%
            summarise(acc = mean(resp))
sum.inv.eff = sub.data %>% group_by(sub, tgt_value, cue_cond) %>%
            summarise(medRT = median(rt)) %>%
            inner_join(acc.data, sum.inv.eff, by=c("sub", "tgt_value", "cue_cond")) %>%
            transform(inv_eff = medRT/acc)

```


```{r, warning=FALSE, fig.align='center' }
line.plot(sum.inv.eff, dv="inv_eff", iv="tgt_value", grp="cue_cond", ylims =c(0.4, 0.92), cols = c(wes_palette("Royal1"),wes_palette("Royal1")))
```


